Multispecies survey for diet comp

### 2020-11-18 SurveyDietCompTest.Rmd
add Kerim's diet code and outline of new sample_diet

>>>>

We want `sample_diet()` to give us something like we would get out of the survey sampling process. The diet sampling function could return diet proportions by predator, including unknown/family level id, with observation error. This would then be input into the models. True diets will be the actual consumption in tons output from `load_detailed_diet_comp()`.

The current partial `sample_diet()` function needs to change because it expects a wide format file of diet proportions, rather than a long-format file of consumption in tons which is the output of `create_survey_diet()`.

It would be nice if `sample_diet()` could take either the output of `load_diet_comp()` (global proportions not surveyed, long format) or `create_survey_diet()`.

The current function removes predators not expected on a fish trawl survey, removes prey types that are normally not counted, then adds uniform error to half the remaining diet proportions, removes a random subet of prey accounting for <0.25 diet proportion, then renormalizes. I would rather have a function that could be used on any "survey" so have already removed hardcoded predator selection. I think also the distributional assumptions need revision; a Dirichlet seems most appropriate to simulate continuous proportions.

```{r, scratch-samplediet, eval=FALSE}

sample_diet <- function(dat, fgs) {

  # read in dat, long format output of load_diet_comp, or create_survey_diet, both have layers aggregated

  # load_diet_comp has no polygon information and is proportion, create_survey_diet has polygons and is consumption in tons

  # first aggregate to global diet comp in proportion

  # then apply aggregation bias

  # then apply Dirichlet obs error; Dirichlet equivalent of rmultinom(1, effN, trueagecomp)?   
  # see e.g., https://rdrr.io/cran/DirichletReg/man/Dirichlet.html

  # returns diet proportions with observation error: Dirichlet, and bias from unknown id and/or family level aggregation

  return(dietprop)
}

  # old function below
  # # first remove species not sampled and not quantified in gut analyses
  # colnames(fgs) <- tolower(colnames(fgs))
  #
  # # check for GroupType or InvertType
  # if (!("grouptype" | "inverttype") %in% colnames(fgs)) {
  #   stop(paste("The columns GroupType  or InvertType ars not in your functional\n",
  #     "groups file and thus sample_diet does not know which groups to sample."))
  # }
  #
  # # change inverttype to grouptype, contents should be the same
  # if("inverttype" %in% names(fgs)) names(fgs)[names(fgs) == 'inverttype'] <- 'grouptype'
  #
  # fgs$grouptype <- tolower(fgs$grouptype)
  # nonsampledtypes <- c("bird", "mammal", "cep", "sed_ep_ff", "sed_ep_other",
  #   "mob_ep_other", "pwn", "lg_zoo", "lg_inf", "phytoben")
  # nonSampled <- subset(fgs, isfished == 0 | grouptype %in% nonsampledtypes |
  #   code == "REP")
  # notenumeratedtypes <- c("bird", "mammal", "cep", "sed_ep_other", "lg_zoo",
  #   "lg_inf", "phytoben")
  # notEnum <- subset(fgs, grouptype %in% notenumeratedtypes | code == "BFF")
  #
  # dat <- dat[!(dat$Predator %in% nonSampled), !(colnames(dat) %in% notEnum)]
  #
  # # add uniform error to half of the "observations"
  # nPreyObs <- NROW(dat) * (NCOL(dat)-1)
  # for(obs in 1:(nPreyObs/2)){
  #   # determine row and column indices
  #   rowR <- sample(1:NROW(dat), 1)
  #   colC <- sample(2:NCOL(dat), 1)
  # 
  #   dat[rowR, colC] <- dat[rowR, colC] + runif(1, -0.1, 0.1)
  # }
  # 
  # # add bias by removing little-observed prey at random
  # for(i in 1:NROW(dat)){
  #   for(j in 2:NCOL(dat)){
  #     if(dat[i,j] < 0.25 & runif(1) < 0.15){
  #       dat[i,j] <- 0
  #     }
  #   }
  # }
  # 
  # # recalibrate so that rows add to 1
  # # first need to adjust/account for negative values
  # baseAdd <- min(dat[,2:NCOL(dat)])
  # if(baseAdd < 0){
  # 
  #   for(i in 1:NROW(dat)){
  #     for(j in 2:NCOL(dat)){
  #       if(dat[i,j] != 0){
  #         dat[i,j] <- dat[i,j]-baseAdd
  #       }
  #     }
  #   }
  # 
  #   }
  # 
  # 
  #   for(r in 1:NROW(dat)){
  # 
  #     denom <- rowSums(dat[r,2:NCOL(dat)])
  #     dat[r,2:NCOL(dat)] <- (dat[r,2:NCOL(dat)])/denom
  #   }

```{r, test-samplediet}
